### 2019-01-13 writing/thesis/chapters/results.tex
Begin work on results.

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.55\\
3 & 3.43 & 3.40 & 3.44\\
4 & 4.44 & 4.44 & 4.67\\
5 & 5.37 & 5.34 & 5.28\\
6 & 5.43 & 5.42 & 5.30\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htb]
  \centering
  \includegraphics{thesis_convergence}
  \caption{$L_2$-Error vs.\ Grid Size.
    The dashed lines are the optimal order of convergence $N+1$.
  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
  \label{fig:convergence-l2-error}
\end{figure}

@@

\section{Accurate CFD}
Show:
\begin{itemize}
\item Taylor-Green High Order
\item ABC Medium Order
\end{itemize}
\section{Accurate Clouds}
\begin{itemize}
\item Cosine Bubble
\item Two Bubbles
\end{itemize}
\section{Time-to-solution: AMR vs Static Mesh}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.

To ensure a fair comparison, we ran both configurations with the same optimisation option.

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
\todo{Noisy, show results}
The best median performance was achieved by using six background threads.

\section{Reactive Euler \textit{\&} Navier Stokes}
\begin{itemize}
\item With viscous effects
\item Without viscous effects  
\end{itemize}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

>>>>

\chapter{Results}\label{chap:results}
\section{Convergence Test}\label{sec:results-convergence}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.55\\
3 & 3.43 & 3.40 & 3.44\\
4 & 4.27 & 4.27 & 4.36\\
5 & 5.00 & 5.02 & 5.08\\
6 & 4.46 & 4.50 & 4.65\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htb]
  \centering
  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
  \caption{$L_2$-Error vs.\ Grid Size.
    The dashed lines are the optimal order of convergence $N+1$.
  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
  \label{fig:convergence-l2-error}
\end{figure}

@@

\section{Accurate CFD}
Show:
\begin{itemize}
\item Taylor-Green High Order
  LIC, Plot v/p ana vs.\ real
\item ABC Medium Order
  Plot p ana.\ vs real
\item Lid-Driven Cavity
  Show LIC, maybe plot over x?
\end{itemize}

\sidetitle{Taylor-Green Vortex}
We use an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
The simulation ran for \SI{10}{\s}.
Our solution results in the expected streamlines (figure xx).
Furthermore, we compare our results with the analytical solution for the incrompressible case.
We achieve a small error (figure xx) for both pressure and velocity.
The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
Overall, we notice a very good agreement with the results of~\cite{dumbser2016high} and the analytical solution.

\sidetitle{ABC Flow}
We use an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
We run the simulation for \SI{1}{\s}.
Figure xxx shows two slices of the simulation, figure xxx compares our numerical approximation of the pressure to the analytical solution.
Again, our solution agrees with the analytical solution.

\sidetitle{Lid-Driven Cavity}
We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
The streamlines agree with the expected solution but have two additional, smaller vortices in the bottom corners.
They do not appear in DUMBER but do appear in OTHERSOLUTION.
Additionally, we show a slice of the velocity in figure XXX, which also agrees with the solution of XXX.
Surprisingly, the limiter was not activated at all.
We noticed that we need the limiter when decreasing the speed of sound. 
The results for this scenario also agree with comparable reference solutions~\cite{ghia1982high}.

\section{Accurate Clouds}
\begin{itemize}
\item Cosine Bubble
\item Two Bubbles
\end{itemize}
Show bubbles, mention they look similar
\section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $27 \times 27$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left(\SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable for this scenario.
This is why we only report an \amr{} run with one level of dynamic refinement.

For both settings, we use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
\todo{Noisy, show results}
The best median performance was achieved by using six background threads.

To ensure a fair comparison, we ran both configurations with the same optimisation options:
\begin{verbatim}
"architecture": "hsw",
"shared_memory": {
    "cores": 28,
    "background_job_consumers": 6,
    "properties_file": "sharedmemory.properties",
    "autotuning_strategy": "dummy"
},
"optimisation": {
    "fuse_algorithmic_steps": true,
    "fuse_algorithmic_steps_factor": 0.99,
    "spawn_predictor_as_background_thread": true,
    "spawn_amr_background_threads": true,
    "spawn_update_as_background_thread": true
}
\end{verbatim}
for the time-to-solution test.
For this we ran the simulation without plotters.
The \amr{}-method took \SI{98654.1}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
while the fully refined grid took \SI{169071}{\s} (\SI{1}{\day} \SI{22}{\hour} \SI{57}{\minute} \SI{51}{\s}).
In other words, the latter method took over 71\% longer.

\section{Reactive Euler \textit{\&} Navier Stokes}
As a final benchmark, we use the reactive Navier-Stokes equations.
We use a limiting \aderdg{}-scheme with an order of 3 and a meshsize of $81 \times 81$.
For some runs, we use the \textsc{cmp}\todo{Refer to dmp equation (and include it)} with the following settings:
\begin{verbatim}
"limiter": {
    "dmp_observables": 3,
    "dmp_relaxation_parameter": 0.05,
    "dmp_difference_scaling": 1e-3,
    "helper_layers": 1
}
\end{verbatim}
We use $\Qrho, \pressure$ and $\QZZ$ as \textsc{dmp} variables.
The results for runs with and without \textsc{dmp} can be seen in figure XXX.
Note, that oscillations diminish the results but are healed by the \textsc{dmp}-criterion.
This scenario shows the differences between the viscous Navier-Stokes equations and the Euler equations clearly:
The viscous effects smooth out the otherwise sharp curves.

It is difficult to compare these results with our references, because they both use different settings.
In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects, \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
We can see that our simulation captures the overall behaviour of the reaction similar to~\cite{helzel2000modified} while the viscous effects show the same tendency as the results from~\cite{hidalgo2011ader}.

Plots-TODO:
\begin{itemize}
\item 2D: Mass fraction
\item 2D: Pressure + Limiter
\item 1D: Line plot pressure
\item 1D: Line plot mass fraction
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
